---
Rtitle: "Projet Final"
author: "Samuel CHICHA"
date: "10/03/2020"
output: pdf_document
params:
  pokemon: "Persian"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#Checking if library is well imported and install them if not
if(!require(readr)){
  install.packages("readr")
  require(readr)
}
if(!require(dplyr)){
  install.packages("dplyr")
  require(dplyr)
}
if(!require(ggplot2)){
  install.packages("ggplot2")
  require(ggplot2)
}
if(!require(fmsb)){
  install.packages("fmsb")
  require(fmsb)
}
#Checking if dataset exists and download it if not
if(!file.exists("data/pokemon.csv"))
  download.file(url = "https://courses.datacrunch.sh/courses/intro-analyse-r/TD6/pokemon.csv", destfile = "data/pokemon.csv", mode = "wb")
pokemons <- read_csv("data/pokemon.csv")
```

# Base de données

```{r intro_bd, echo=FALSE}
#Computing number of generations, pokemons and legendary ones
nb_gen <- length(unique(pokemons$Generation))
nb_pokemons <- nrow(pokemons)
nb_leg <- nrow(pokemons[pokemons$Legendary == TRUE,])
picked <- params$pokemon
```

La base de données présente une liste de `r nb_pokemons` pokémons étalés sur `r nb_gen` générations dont `r nb_leg` sont légendaires. 
Nous étudierons ici le pokémon "`r picked`".

# Etude du pokémon

```{r intro_persian, echo=FALSE}
#Getting the pokemon we picked
pokemon <- filter(pokemons, Name == picked)
```
>
> __Nom__: `r pokemon$Name`
>
> __Type__: `r pokemon$'Type 1'`
>
> __Points de vie__: `r pokemon$HP`
>
> __Attaque__: `r pokemon$Attack`
>
> __Defense__: `r pokemon$Defense`
>
> __Attaque spécial__: `r pokemon$'Sp. Atk'`
>
> __Défense spécial__: `r pokemon$'Sp. Def'`
>
> __Vitesse__: `r pokemon$Speed`

```{r first_comparison, echo=FALSE}
#Getting pokemons of the same generation than the one we picked
same_gen_pokemons <- filter(pokemons, Generation == pokemon$Generation)
#Creating column to aggregate on
result.min <- cbind("Min", min(pokemons$HP), min(pokemons$Attack), min(pokemons$Defense), min(pokemons$`Sp. Atk`), min(pokemons$`Sp. Def`), min(pokemons$Speed))
colnames(result.min) <- colnames(same_gen_pokemons[4:10])
#colnames(result.min$) <- "Name"
#result.max <- aggregate(pokemons[5:10], list(pokemons$tmp), max)
#result.mean <- aggregate(pokemons[5:10], list(pokemons$tmp), mean)
```

# Battre Lugia